---
title: "Document title"
subtitle: "
This is a space dedicated to the sub-title/Abstract to the report
<br/>
"
footer: Epicentre - Médecins Sans Frontières
format: 
  epitemplates-report-html: 
    logo1: img/epicentre_msf_logo_transparent.png
    logo2: img/bnitm_logo.png
author:
  - name: Author 1
    email: email.author.1@epicentre.msf.org
  - name: Author 2
    email: email.author.2@epicentre.msf.org
github-repo: "https://github.com/epicentre-msf" 
date: last-modified
date-format: long
comments:
  hypothesis: true
---

# primary 

```{r setup}
#| include: false

# library(fs)         # work with path
# library(here)       # create relative paths
# library(rio)        # import files
# library(janitor)    # data cleaning
# library(lubridate)  # date handling
# library(tidyverse)  # data science 

```


## secondary 

### tertiary

#### Quatery

# Formatting

1. *Italic* and **Bold** will turn out like this

2. Tooltip are trickier to use than in a normal `.Rmd` not set-up here yet

3. Inline coding will turn out `like this`

4. You can also annotate and comment the text. This requires an account on [Hypothes.is](https://web.hypothes.is/)

5. [This is how an hyperlink renders](https://epicentre-msf.github.io/gallery/)

## Callouts

::: {.callout-note}
**This is a Note** using `{.callout-note}`
:::

::: {.callout-caution}
**This is a warning** using `{.callout-caution}`. They can be collapsed using `collapse="true"` 
:::

::: {.callout-important}
**This is an important note** using `{.callout-important}`
:::

> This is a `blockquote` made using `>` 

::: {.cell .page-columns .page-full .column-screen .grey-section}
You can also add a grey section on full page using: `{.cell .page-columns .page-full .column-screen .grey-section}`
:::

### Global options

```{yaml}
#| eval: false
# Use this global options in YAML to hide all code chunks
---
execute: 
  echo: false 
---
```


### Panels 

You can put several graphs next to one another with `{.panel-tabset .nav-pills}`

::: {.panel-tabset .nav-pills}
## Panel 1

Here goes one thing

## Panel 2

and here a second 

:::

### Value boxes 

You can add some pretty useful value boxes with `{bslib}`

:::{.column-page}

::: {.grid}

::: {.g-col-12 .g-col-md-4}
```{r, echo = FALSE}
bslib::value_box(
  title = "Total Screenings",
  value = scales::number(100000, na.rm = TRUE),
  showcase = bsicons::bs_icon("card-checklist"),
  theme = "primary"
)

```
:::

::: {.g-col-12 .g-col-md-4}
```{r, echo = FALSE}
bslib::value_box(
  title = "Total Enrolments",
  value = scales::number(120333, na.rm = TRUE),
  showcase = bsicons::bs_icon("person-add"),
  theme = "primary"
)
```
:::

::: {.g-col-12 .g-col-md-4}
```{r, echo = FALSE}
bslib::value_box(
  title = "Total Month 2 Visits",
  value = scales::number(300000, na.rm = TRUE),
  showcase = bsicons::bs_icon("box-arrow-right"),
  theme = "primary"
)
```
:::

:::

:::
