---
title: "Document title"
subtitle: Epi-DS team - Epicentre, Paris
footer: Epicentre - Médecins Sans Frontières
format: 
  epitemplates-report-html: default
author:
  - name: Author 1
    email: email.author.1@epicentre.msf.org
  - name: Author 2
    email: email.author.2@epicentre.msf.org
date: last-modified
date-format: long
toc: true
comments:
  hypothesis: true
---

```{r setup}
#| include: false

# library(fs)         # work with path
# library(here)       # create relative paths
# library(rio)        # import files
# library(janitor)    # data cleaning
# library(lubridate)  # date handling
# library(tidyverse)  # data science 

```

# Primary title

1. *Italic* and **Bold** will turn out like this

2. Tooltip are trickier to use than in a normal `.Rmd` not set-up here yet

3. Inline coding will turn out `like this`

4. You can also annotate and comment the text. This requires an account on [Hypothes.is](https://web.hypothes.is/)

## Secondary title

::: {.callout-note}
**This is a Note** using `{.callout-note}`
:::

::: {.callout-caution}
**This is a warning** using `{.callout-caution}`. They can be collapsed using `collapse="true"` 
:::

::: {.callout-important}
**This is an important note** using `{.callout-important}`
:::

> This is a `blockquote` made using `>` 

### Tertiary title

```{yaml}
#| eval: false
# Use this global options in YAML to hide all code chunks
---
execute: 
  echo: false 
---
```

# Add value box with `bslib`

:::{.column-page}

::: {.grid}

::: {.g-col-12 .g-col-md-4}
```{r, echo = FALSE}
bslib::value_box(
  title = "Total Screenings",
  value = scales::number(100000, na.rm = TRUE),
  showcase = bsicons::bs_icon("card-checklist"),
  theme = "primary"
)

```
:::

::: {.g-col-12 .g-col-md-4}
```{r, echo = FALSE}
bslib::value_box(
  title = "Total Enrolments",
  value = scales::number(120333, na.rm = TRUE),
  showcase = bsicons::bs_icon("person-add"),
  theme = "primary"
)
```
:::

::: {.g-col-12 .g-col-md-4}
```{r, echo = FALSE}
bslib::value_box(
  title = "Total Month 2 Visits",
  value = scales::number(300000, na.rm = TRUE),
  showcase = bsicons::bs_icon("box-arrow-right"),
  theme = "primary"
)
```
:::

:::

:::
